### 2022-08-02 main/chapter_2ljets.tex
remove top other todo

\paragraph{Sub-processes}
\TODO{sort out top other label}
Our high-level sample labels such as $\ttbar$, $\zjets$, diboson and
rare-top (`Top other') each include many sub-samples that are physically
distinct and non-interfering.
Highlights from a study of the contributions from these sub-samples are
presented in Figure~\ref{fig:2ljets_splits}.

>>>>

\paragraph{Sub-processes}
Our high-level sample labels such as $\ttbar$, $\zjets$, diboson and
rare-top (`Top other') each include many sub-samples that are physically
distinct and non-interfering.
Highlights from a study of the contributions from these sub-samples are
presented in Figure~\ref{fig:2ljets_splits}.
